The imprint of global magma oceans on exoplanet demographics

### 2022-11-23 src/tex/ms.tex
add a (preliminary) bullet-point list of conclusions

\begin{note}
    \textit{Here or in the introduction:} For observations of rocky exoplanets, the currently best-probed regime that of hot, close-in planets.
    These bodies experience climatic conditions that are similar to the environment of the inner Solar System bodies at early stages of their formation.
    Studies of the geophysical state and evolution of hot exoplanets can thus contribute to our understanding of the early formation stages of Earth and other habitable worlds.
\end{note}

>>>>

\begin{note}
    \textit{Here or in the introduction:} For observations of rocky exoplanets, the currently best-probed regime is that of warm, close-in planets.
    These bodies experience climatic conditions that are similar to the environment of the inner Solar System bodies at early stages of their formation.
    Studies of the geophysical state and evolution of hot exoplanets can thus contribute to our understanding of the early formation stages of Earth and other habitable worlds.
\end{note}

The key findings of our work are as follows:
\begin{enumerate}
    \item Planetary radius changes due to the combined effect of steam atmospheres and water dissolved in the molten mantle of planets within the runaway greenhouse threshold is expected to cause a discontinuity in the radius distribution of small (DEFINITION) exoplanets.
    \item Since XXX\SI{}{\percent} of confirmed exoplanets in this size range are in the runaway greenhouse regime, we suggest that this imprint is detectable with transit measurements of a large enough sample and sufficient precision.
    \item Using Bioverse, we find that the planned PLATO transit survey will provide a sufficient sample to test the magma ocean hypothesis.
    \item The diagnostic power of transit missions in testing this hypothesis can be maximized by ...
    \item A detection of the feature will constrain the water inventory of rocky exoplanets, providing important context in the assessment of their habitability.
\end{enumerate}
